Markov Link Method for combining knowledge from destructive measurements

### 2018-04-04 trygve/paper.tex
changed caption

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/allenRUX}
\caption{10 Rotationally Uniform eXtremal samples from the polytope $\hat \Theta$.  These extremal samples from $\hat \Theta$ have quite a lot in common.  The common features are ones that we can feel confident are present in the true value of the joint distribution, $q^*$.  Other entries have more variability; these suggest specific experiments which might help disambiguate how technique I and technique II are related through $q^*$.  \label{fig:allenRUX}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/allenRUX}
\caption{Output: 10 Rotationally Uniform eXtremal samples from the set $\hat \Theta$.  Each sample shows a different way that technique I might line up with technique II; all of them are consistent with the observed data.  Note that these extremal samples from $\hat \Theta$ have quite a lot in common.  The common features are ones that we can feel confident are present in the true value of the joint distribution, $q^*$.  Other entries have more variability; these suggest specific experiments which might help disambiguate how technique I and technique II are related through $q^*$.  \label{fig:allenRUX}}
\end{figure}
